The initial chapters laid the groundwork by illustrating the critical role of cooling technologies in addressing the pressing issues of global warming and the energy crisis. With an emphasis on PDRCs, we embarked on a journey through the theoretical underpinnings and practical applications of these devices, which offer the potential for efficient, energy-free cooling by radiating heat directly to outer space during daylight hours.

Throughout this exploration, we leveraged the capabilities of COMSOL Multiphysics™ to simulate various PDRC configurations, aiming to enhance their performance by optimizing material properties and layering strategies. The results chapter validated our approach, demonstrating the effectiveness of PDRCs in achieving significant cooling effects under real-world conditions.

As we culminate this research, this concluding chapter aims to distill the insights gained from our investigations, outlining the contributions of this work to the field of cooling technologies and the broader context of sustainable energy solutions.

\section{Our work}

COMSOL Multiphysics \texttrademark \space has proven itself as an indispensable tool for computational modeling, facilitating the simulation of intricate PDRC structures with relative ease. The modeling approach, exemplified in Chapter 3 through a detailed walkthrough with a busbar example, laid the foundation for all subsequent simulations.

This thesis has not only corroborated established theoretical principles within the realms of anti-reflectivity and high reflectance but has also ventured into the modeling of Fresnel equations to observe the behavior of reflection coefficients across varying angles of incidence.

The core of our efforts was the computational modeling of PDRC designs from Hudgings Lab, layer by layer, revealing critical insights into their optical performance. Notably, the simulation results confirmed the imperative for PDRCs to exhibit high reflectivity within the solar spectrum, a requirement clearly illustrated by the limited reflectivity observed in the sole glass substrate model.

\section{Future Directions}

Moving forward, several avenues for further research have been identified:

\begin{enumerate}
    \item Enhanced definition in the reflectance versus wavelength graphs for glass plus silver and glass plus silver plus PDMS models, possibly through the utilization of more detailed refractive index interpolation tables or functions.
    \item Exploration of adding more materials on top of the PDMS layer to fulfill PDRC design criteria more effectively, experimenting with various thicknesses and refractive indices to exploit constructive interference across multiple interfaces more efficiently.
    \item The translation of computational models into physical prototypes for empirical validation in lab settings, comparing simulated reflectance with real-world performance.
    \item Development of reflectance versus angle of incidence models to aid in the characterization of PDRC behavior throughout the day, providing a benchmark for experimental testing on rooftop installations.


% TODO: Format this to suit the format of the rest of the future work section

By strategically adjusting these parameters, it is possible to shift the stopband's center, enhancing the filter's spectral transmittance across a broader range. This capability to finely control the light's passage through these structures not only underscores the versatility of DBRs but also paves the way for their integration into a wide array of optical devices, where precise manipulation of light is paramount \cite{pedrotti_introduction_2007}.

Building on the principles of DBRs and their implications for enhanced reflectivity, a parallel can be drawn to PDRCS. PDRCs, which aim to achieve cooling without energy input by radiating heat into the cold outer space, can significantly benefit from the reflective properties and spectral selectivity offered by DBR structures.

PDRCs leverage similar concepts to reflect the solar spectrum while allowing the thermal infrared range to pass through effectively. By incorporating multilayer structures like those used in DBRs, PDRC devices can optimize their performance, achieving a delicate balance between high solar reflectance and high thermal emittance. This enables PDRC systems to reflect the majority of incoming solar radiation, minimizing heat absorption, while simultaneously maximizing the emission of infrared radiation for cooling.
\end{enumerate}

\section{Final Remarks}

This thesis not only validates the utility of PDRCs within the context of sustainable cooling technologies but also charts a course for their further development and application especially on the computational modeling front.

As we look to the future, the insights and methodologies presented here will serve as a valuable resource for those endeavoring to advance the efficiency and applicability of PDRCs and similar technologies in our collective pursuit of environmental sustainability and energy efficiency.